BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-14 tex/5-evaluation.tex
Compiled

In addition to the extraction of blog content that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.

As presented in section \autoref{techniques}, our crawler uses a full web browser to render pages.

To achieve this property, our final solution was to embed a full web browser into our system, , which we use to take screen-shots of pages. Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath. This subsection relates our evaluation of these tools for the specific purpose.

@@

\cmark
\xmark

functionality |  wget  | wkhtmltopdf | oxpath | phantomjs
---------------------------------------------------------
js support    |        |             |        |
page interat  |   n    |      n      |   y    |    y
js support    |   n    |      y      |   y    |    y
running time  | 0.50s  |    7.58s    | 22.04s |  3.32s

>>>>

Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}. Our final solution consists in taking a screenshot with our embeded web browser after the JavaScript rendering. Before opting for this approach, we considered 3 other solutions: GNU Wget, wkhtmltopdf and OXPath. This subsection relates our evaluation of these tools for the specific purpose.

@@

\savevisualsTable
